---
title: "Week 02: COVID Visualization Activity"
author: "**`[[`**Your Name**`]]`**"
format: gfm
---

Today, we'll be working with a data set related to COVID.
This data is based on data from the the [COVID Tracking Project](https://covidtracking.com/).
I cleaned up this data and also added total populations from the 2020 for each of the relevant categories.
Note, due to differences in the way race and ethnicity are encoded in the census as compared to the the COVID Tracking Project, the population counts for LatinX may be somewhat inaccurate.

```{r load_data}
library(tidyverse)
load("CRDT Data.RData")
ls()
```

I've included 5 different data sets.
The data `covid_data_count`, `covid_data_long`, `covid_data_orig`, and `covid_data_race` all have the same data but have it represented in different ways.

The `covid_data_simple` has a substantially simplified version of the data.
(Within a few weeks you'll be able to create each of these data sets from the `covid_data_orig` file yourself.)

Start by exploring using different `geom`s, aesthetics, facets, etc.


```{r first_plot}
ggplot(covid_data_count, aes(x = date, y = Cases)) + geom_point()
```



If you want to only look at a specific state, you can do it like this.
For now, see what you can do just using `ggplot`.

```{r}
covid_data_count |> 
  filter(state == "MA") |> 
  ggplot(aes(x = date, y = Cases, color = race)) + geom_line()
```

## Exercise for next time


**Goal** Make a plot showing the cumulative number of deaths per 100,000 people across time among each race group in the `covid_data_simple`. You only need to use `ggplot`. To get started, you can use this code block.


```{r exercise}
ggplot(covid_data_simple, aes(x = date, y = Deaths)) + geom_point()
```

Comment on the disparities between the race groups.

**When you finish**
Either

* Work to polish and improve the the plot you created by incorporating titles, better labels, scales, annotations, etc.

or 

* Try to create your own plot. Write code for a plot and describe what you observe. Are there any conclusions you can draw?
